Implementing XBF: An Efficient Self-Describing Binary Format

### 2023-08-08 docs/paper.tex
Add latest paper changes to ensure they aren't lost

On the web, data is largely interchanged in one of two formats, XML (Extensible Markup Language)\cite{xml} or JSON (JavaScript Object Notation)\cite{json}. These formats have two key features that have led to their popularity, human-readability and being self-describing. These features have inherent inefficiencies, which XBF (Xtensible Binary Format)\cite{xbf_spec} intends to solve by making compromises.

@@

\subsection{Enhancements to be Made}

@@

\begin{IEEEitemize}
	\item Send data and metadata in a binary format (no longer human-readable)
	\item Remain self-describing, but have the option to not include metadata if it's already known
	\item Prioritize simplicity in the type system
\end{IEEEitemize}

@@

\section*{Acknowledgment}

>>>>

On the web, data is largely interchanged in one of two formats, XML (Extensible Markup Language)\cite{xml_spec} or JSON (JavaScript Object Notation)\cite{json_spec}. These formats have two key features that have led to their popularity, human-readability and being self-describing. These features have inherent inefficiencies, which XBF (Xtensible Binary Format)\cite{xbf_spec} intends to solve through carefully chosen compromises.

@@

\subsection{Enhancements Made}

@@

\begin{IEEEitemize}
	\item Send data and metadata in a binary format (no longer human-readable).
	\item Remain self-describing, but have the option to not include metadata if it's already known, and deduplicate metadata whenever possible.
	\item Prioritize simplicity in the type system.
\end{IEEEitemize}

\section{Methodology and Implementation}

\section{Results}

\section{Discussion}

\section{Conclusion}

\section{}

@@
